Ideal model selection is impossible

### 2014-12-08 Facticity/Facticity/paper.tex
gacs

>>>>

\section{Paul's sophistication (total, non-prefix) is \emph{not}  bounded}

Proof sketch:

\begin{itemize}
  \item There is a $C$ such that for every $n$ there are strings $x$
    with $K(S)+\log|S|\ge K(x)+(3/4)n+C$ for all $K(S)>1/4$.

  \item For all $C$ there is an $n$ such that there are $x$ with
    $K(S)+\log(S)<K(x)+C$ only if $K(S)>1/4$.
\end{itemize}
